---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# puncture

<!-- badges: start -->
<!-- badges: end -->

The goal of puncture is to implement a bootstrap-based analysis method. The base method implements the following algorithm for each bootstrap iteration:

- Generate a missingness pattern using the specified
- Apply the pattern to create a dataset with missing values
- Perform multiple imputation
- Fit the specified model to each imputed dataset
- Pool results across imputations using Rubin's rules
- Extract the requested statistics for the term of interest

When the stacking parameter is set to an integer greater than 1, the algorithm is modified to create and combine multiple copies of the dataset before imputation:

- For each of the specified number of stacks:
  - Generate and apply a unique missingness pattern
  - Optionally thin the data by randomly selecting rows (if thin < 1)
- Combine all resulting datasets
- Proceed with multiple imputation and subsequent steps as in the base algorithm


## Installation

You can install the development version of puncture from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("mightymetrika/puncture")
```

## Puncturing 'cars'

This is how pucnture() works with the 'cars' dataset.

```{r example}
library(puncture)

# First use stats::lm() as a reference model
summary(stats::lm(speed ~ dist, cars))

# Now run puncture() as comparison model
set.seed(1913)
pcars <- puncture(cars,
                  b = 10,
                  m = 5,
                  mpat = function(mdat){ # define missing data pattern
                    n <- nrow(mdat) * ncol(mdat)
                    c1 <- stats::rbinom(n, 1, 0.8)
                    c2 <- stats::rbinom(n, 1, 0.8)
                    pattern_vec <- c1 * c2
                    matrix(pattern_vec, nrow = nrow(mdat), ncol = ncol(mdat))
                    },
                  form = "speed ~ dist",
                  term = "dist",
                  func = stats::lm,
                  statistics = c("estimate","p.value"),
                  remove.collinear=FALSE # passed to mice::mice(...)
                  )
hist(pcars$estimate)
mean(pcars$estimate)
median(pcars$p.value)
```
